Multi-level modeling with Openflexo/\FML - A contribution to the \mpc

### 2021-05-31 5-analysis.tex

\noteAntoine{Pourquoi S9 et S13 sont ambigus, quels choix on a fait...}
\todo[inline]{noms pas dans la spec, complètement implicite ; }

We now analyse a few specifications that deserve a comment for the choices we made.

\begin{itemize}
    \item We added an implicit specification (S0) saying that all things have names.
    \item (S9) It is unclear when a tested artefact must be associated to its test report. At the creation of the artefact or of its report? \todo[inline]{We choose\dots}
    \item (S13) [linked to P9] \todo[inline]{We choose ti interpret \dots}
\end{itemize}

>>>>

%\noteAntoine{Pourquoi S9 et S13 sont ambigus, quels choix on a fait...}
%\todo[inline]{noms pas dans la spec, complètement implicite ; }

%We now analyse a few specifications that deserve a comment for the choices we made.

%\begin{itemize}
%    \item We added an implicit specification (S0) saying that all things have names.
%    \item (S9) It is unclear when a tested artefact must be associated to its test report. At the creation of the artefact or of its report? \todo[inline]{We choose\dots}
%    \item (S13) [linked to P9] \todo[inline]{We choose to interpret \dots}
%\end{itemize}

%The analysis of the specification should be presented in this section. However, t
The choices we made are complicated to justify out of context. That is why our choices are presented within the next section model presentation.
